Kindly Bent to Free Us

### 2020-03-04 kindly/intro.tex
extensions

\begin{itemize}
\item A type system encoding linearity and affinity with
  borrowing. The type system is polymorphic for types and
  for kinds that express constraints on the number of uses of a value.
\item An extension of the \hmx framework
  \cite{DBLP:journals/tapos/OderskySW99} with kinds, regions, and
  multiplicity constraints that supports full, principal type inference.
\item Soundness proof of the inference algorithm.
\item Big-step linearity aware semantics with an expressive soundness theorem.
\item Constraint simplification techniques.
\item Automatic inference of regions for borrows.
\item A prototype implementation of the type inference algorithm, including all
  constraint simplification and extended with pattern matching,
  available at \url{https://affe.netlify.com/}.
\end{itemize}

As \lang{} is built on top of the \hmx{} framework, which is a general
framework for expressing constraint-based typing and type inference,
the extension of our work with features like typeclasses, ad-hoc overloading,
traits, etc is possible and orthogonal to the presentation in this paper.

>>>>

\begin{itemize}
\item A type system encoding linearity and affinity with
  borrowing. The type system is polymorphic for types and
  for kinds that express constraints on the number of uses of a value.
\item An extension of the \hmx framework
  \cite{DBLP:journals/tapos/OderskySW99} with kinds, regions, and
  multiplicity constraints that supports full, principal type inference.
\item Soundness proof of the inference algorithm.
\item Big-step linearity aware semantics with an expressive soundness theorem.
\item Constraint simplification techniques.
\item Automatic inference of regions for borrows.
\item A prototype implementation of the type inference algorithm, including all
  constraint simplification and extended with algebraic datatypes and
  pattern matching,
  available at \url{https://affe.netlify.com/}\footnote{This link is safe for double-blind.}.
\end{itemize}

As \lang{} is built on top of the \hmx{} framework, which is a general
framework for expressing constraint-based typing and type inference,
the extension of our work with features like typeclasses, ad-hoc overloading,
traits, etc is possible and orthogonal to the presentation in this paper. 
While the system is geared towards type inference, it is nonetheless
compatible with type annotations and thereby amenable to extensions
where type inference may no longer be possible.
